Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2020-01-29 rnni_convexity.tex
add figure partition lattice

The \emph{partition lattice} on $\{1, \ldots, n\}$ is the lattice given by the partially ordered set $(\Pi_n,\leq)$, where $\Pi_n$ is the power set of $\{1, \ldots, n\}$ and $x \leq y$ if partition $x$ refines $y$.
For simplification we will denote the partition lattice by $\Pi_n$.
We assume that the partition lattice is ranked such that the partition into singletons has rank zero and the set $\{1, \ldots, n\}$ has rank $n-1$.
This algebraic structure is related to the $\rnni$ graph in the following way.

@@

>>>>

The \emph{partition lattice} on $\{1, \ldots, n\}$ is the lattice given by the partially ordered set $(\Pi_n,\leq)$, where $\Pi_n$ is the power set of $\{1, \ldots, n\}$ and $x \leq y$ if partition $x$ refines $y$.
For simplification we will denote the partition lattice by $\Pi_n$, $\Pi_4$ is illustrated in Figure~\ref{fig:partition_lattice4}.
We assume that the partition lattice is ranked such that the partition into singletons has rank zero and the set $\{1, \ldots, n\}$ has rank $n-1$.
This algebraic structure is related to the $\rnni$ graph in the following way.

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{partition_lattice4}
\vspace{12pt}
\caption{The partition lattice $\Pi_4$ on $\{1,2,3,4\}$.
The highlighted edges correspond to an $\rnni$ path from the tree represented by the leftmost chain to the rightmost one.}
\label{fig:partition_lattice4}
\end{figure}
